%\begin{document}
\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
\usepackage{enumerate}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{color}
\usepackage{epstopdf}
\usepackage[printwatermark]{xwatermark}
\usepackage{tikz}

\providecommand{\sol}{\noindent \textbf{Solution: }}
\providecommand{\points}[1]{\textcolor[rgb]{1, 1, 1}{.}\hfill{\textbf{[#1 points]} } \\ }
\providecommand{\grader}[1]{\noindent \textcolor[rgb]{0.5, 0, 0}{\emph{Note to grader:}} #1}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Final review: CH5-8}
%\author{Jeff Lai}

\begin{document}
\maketitle

\begin{enumerate}[Q 1.]
%%%%%%%%%%%%%%%%%%%%%%%%% Question 1 %%%%%%%%%%%%%%%%%%%%%%%%%%
\item  In a sociology graduate's senior thesis, she conducts a study on the number of hours per day JHU students spent on studying. Data is collected from the Freshman, Sophomore, and Junior classes and is listed below.\\

\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Freshman (F)& Sophomore (S)& Junior (J)\\
\hline
3.0 & 4.5 & 6.0\\
2.5 & 3.5 & 4.5 \\
3.5 & 4.0 & 6.0 \\
3.5 & 4.5 & 8.5 \\
3.5 & 4.5 & 6.5 \\
4.0 & 4.5 & 6.0 \\
& &         6.5 \\           
\hline \end{tabular}
\end{center}
Test the hypothesis that the means for all three groups are the same. Use $\alpha=0.05.$

\vspace{35mm} 
%%%%%%%%%%%%%%%%%%%%%%%%% Question 2 %%%%%%%%%%%%%%%%%%%%%%%%%
\item We want to compare the number of seeds in strawberries and watermelons. Assume the populations are normally distributed. A sample of 13 strawberries had a sample variance of 64. A sample of 16 watermelons had a sample variance of 16. Test the null hypothesis at $\alpha = 0.10$ and find the full rejection region. 
$$\text{H}_0: \; \sigma_s^2=\sigma_w^2$$
$$\text{H}_A: \; \sigma_s^2 \neq \sigma_w^2$$

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 3 %%%%%%%%%%%%%%%%%%%%%%%%%
\item A study found that among a sample of 180 banana lovers, 43 of them ($\hat{p}_b$ =  0.2389) reported to be avid collectors. Among 175 interviewed pineapple lovers, 28 of them ($\hat{p}_p$ =  0.16) were avid collectors. Test the following at $\alpha = 0.05$. Find the $p$-value.
$$\text{H}_0: \; p_b \leq p_p$$
$$\text{H}_A: \; p_b > p_p$$
	
\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 4 %%%%%%%%%%%%%%%%%%%%%%%%%
\item A study measured the diameter of strawberries. Assume population is normally distributed. A sample of 30 strawberries had a sample variance of 0.09. Test the null hypothesis at $\alpha = 0.05$. 
$$\text{H}_0: \; \sigma_0^2 \geq 0.14$$
$$\text{H}_A: \; \sigma_a^2 < 0.14$$

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 5 %%%%%%%%%%%%%%%%%%%%%%%%%
\item A soda company states that the sugar content in their bottles is normally distributed. A sample of 36 soda bottles are tested for sugar content. It is found that this sample has an average of $\bar{x} = 69.2$ grams of sugar per bottle. Test the null hypothesis regarding the sugar contained in all soda bottles of this kind:
$$\text{H}_0: \; \mu = 68$$

Versus the alternative hypothesis:
$$\text{H}_a: \; \mu \neq 68$$

It is known that the population standard deviation, $\sigma = 3.6$ grams. Use $\alpha = 0.01$, and find the $p$-value.
	
\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 6 %%%%%%%%%%%%%%%%%%%%%%%%%
\item Assume that the life expectancy are normally distributed in countries A and B. We do not know the variance of life length, but we know that they are equal in these nations. Suppose that 15 death certificates are obtained in Country A have $\bar{x}_A = 64$ years with $s_A = 3$, while 12 certificates in Country B have $\bar{x}_B = 68$ years and $s_B = 2.5$. Test the null hypothesis regarding the difference in means:
$$\text{H}_0: \; \mu_A - \mu_B = 0$$

Versus the alternative hypothesis:
$$\text{H}_a: \; \mu_A - \mu_B \neq 0$$

Use $\alpha = 0.02$.
	
\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 7 %%%%%%%%%%%%%%%%%%%%%%%%%
\item
The response of a new diabetic drug was measured for 20 patients at Johns Hopkins Hospital (group 1) and 15 control subjects (group 2). The sample variance for group 1 is $s_1^2 = 100$, and the sample variance for group 2 is $s_2^2 = 120$. Construct the 95 \% confidence interval for the population variances: $\frac{\sigma_1^2}{\sigma_2^2}$. 

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 8 %%%%%%%%%%%%%%%%%%%%%%%%%
\item Given a p-value of 0.001: 
	\begin{enumerate}[(a)]
	\item Find the range of $\alpha$ such that the null hypothesis can be rejected. 
	\item Find the range of $\alpha$ such that the null hypothesis cannot be rejected.
	\end{enumerate}
	
\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 9 %%%%%%%%%%%%%%%%%%%%%%%%%
\item Consider a population quality of unknown distribution but with known $E(X) = \mu$ and $\var(X) = \sigma^2$. If we take a sample of size $n = 100$, is it true that: 
\[ \frac{\overline{X} - \mu}{\frac{\sigma}{\sqrt{n}}} \sim N(0,1)? \]
Answer yes or no. If no, either give the correct distribution or state that it cannot be determined.\\

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 10 %%%%%%%%%%%%%%%%%%%%%%%%
\item Consider a population quality of unknown distribution but with known $E(X) = \mu$ and $\var(X) = \sigma^2$. If we take a sample of size $n = 10$, is it true that: 
\[ \frac{\overline{X} - \mu}{\frac{\sigma}{\sqrt{n}}} \sim N(0,1)? \]
Answer yes or no. If no, either give the correct distribution or state that it cannot be determined.\\

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 11 %%%%%%%%%%%%%%%%%%%%%%%%
\item Now consider two different populations. We take one sample from each of sizes $n_1 = 16$ and $n_2 = 25$ to measure their heights in feet, and determine that the sample means $\bar{x}_1 = 6$ and $\bar{x}_2 = 5.5$, and the sample variances $s_1^2 = s_2^2 = 0.25$. Assume the population variances are equal.
	\begin{enumerate}
	\item Compute the 95 \% confidence interval for the difference of population mean heights.
	\item Compute the 90 \% confidence interval for the difference of population mean heights.
	\end{enumerate}

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 12 %%%%%%%%%%%%%%%%%%%%%%%%
\item Let $X$ be a binomial distribution with $n=20$ and $p=0.25$. What is the probability that $X \geq 8$ ? Find the answer using a normal approximation with a continuity correction. 

\vspace{35mm}
%%%%%%%%%%%%%%%%%%%%%%%%% Question 13 %%%%%%%%%%%%%%%%%%%%%%%%
\item Suppose 30\% of people in a population own dogs. Scientists drew a sample of size 50 from this population. Let $\hat{p}$ be the proportion of the sample who are dog owners. (You do not need to take into account continuity correction.)
\begin{enumerate}[(a)]
\item Find the mean of $\hat{p}$.
\item Find the standard error of $\hat{p}$, i.e find $\sigma_{\hat{p}}$.
\item What is the probability that $\hat{p} \geq 0.4$ ?
\end{enumerate}

\vspace{35mm}

\end{enumerate} 
\end{document}